---
title: "Public office"
author: "Ian Lindell"
date: "5/17/2019"
output: html_document
---

```{r setup, warning=FALSE, message=FALSE, echo=FALSE}
library(knitr)
address <- "Seattle, WA"
state <- substr(address, nchar(address) - 1, nchar(address))
library(ggplot2)
library(dplyr)
source("api-keys.R")
source("civic-info.R")
source("propublica.R")
```

## Your Representatives
This report contains a list of people who hold public office for the given address, **`r address`** from state to national level. Data for this list was gathered from _[ProPublica API](https://projects.propublica.org/api-docs/congress-api/)_ and _[Google Civic Information API](https://developers.google.com/civic-information/)_.

```{r echo=FALSE}
kable(table, "html") %>%
  kable_styling(full_width = F)
```

## House of Representatives

Here are two charts that show members of the House by gender and political party. 
```{r echo=FALSE}
gender_plot
```

```{r echo=FALSE}
party_plot
```

Lets take a closer look at one representative, `r name`. She is `r age` years old, and you can find her on twitter at [`r twitter_link`](https://twitter.com/RepDelBene). Of the last 20 congressional votes she voted with the majority `r agree / 20 * 100`% of the time.
